The Power of Two Random Choices

### 2014-01-13 article/article.tex
application: online load balancing

\subsection{On-line load balancing}

>>>>

\subsection{Online load balancing}
The following simple scenario is a typical application of online load balancing: Consider $n$ servers\footnote{Such as file-, database- or network servers} and $m$ requests issued by clients that need to be handled by these servers. For simplicity, assume that each task can be handled by any server and that all tasks are of the same size, i.e., require the same amount of execution time.

To maximize the throughput of the servers, a uniform distribution of tasks to servers is desireable. This can easily be achieved by a central dispatcher. However, such a central dispatcher poses a bottleneck within a distributed system and querying $m$ servers for their current load involves significant overhead, e.g., sending a message to each server and waiting for the reply and more efficient solutions are neccessary. As with hashing, the balls-into-bins model can be applied easily: we need to assign tasks (the balls) to servers (the bins). Assuming tasks are assigned to servers uniformly and independently at random, the two-choice paradigm is directly applicable: If each client samples two random servers for their load and sends issues its request to the least loaded server, the overhead is comperatively small and the difference in load on the $n$ servers is bounded by $\Theta\left(\log \log n\right)$ w.h.p. \cite{RS98} \cite{MRS01} \cite{KLM92}.
